\huge{DRAFT} \\ ~\\ \Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project

### 2014-06-14 articles/2014/whisper/aricleEbauche/Draft_BriandBzeznikIrodsUserMeeting2014.tex
add Introduction, conclusion and references

\begin{document}
\long\def\/*#1*/{}
\date{}%{\today}
\title{\huge{DRAFT} \\ ~\\ \Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project}
\author{\begin{tabular}[t]{c@{\extracolsep{8em}}c}
	Briand Xavier\footnote{Cnrs, Isterre, Whisper, email xav.briand@gmail.com}  & Bzeznik Bruno\footnote{Ciment, Universit\'e Joseph Fourier, Technical header of Ciment} \\
\end{tabular}}
\maketitle
%\thispagestyle{empty}

\subsection*{Abstract}
{\em

Like many projects in science of the universe, the seismological project Whisper is faced with massive data processing.
This leads to specific IT software for the project as well as suitable IT infrastructure. We present here both aspects.

We provide a flexible way to design a sequence of processing. We also deal with data-management and computational optimization questions.

On IT infrastructure, we present the platform Ciment provided by the University of Grenoble. It offers a data-grid environement with the 
distributed storage iRODS and the grid manager CiGri.

This is the partnership between these two IT components that has enabled a data-intensive processing and, also,  permits to the Whisper project to bring new scientific results.

}
{\bf Keywords}:  Data-Intensive, grid computing, distributed storage, Seismic Noise, Whisper, Cigri, Irods.

@@

\newpage
\section{Background}% 7-10\S, 1-2 pages}

@@

In addition, the calculation operations downstream may produce even more data than the observation data.
To give an order of magnitude, more than 200 TB have to be processed by the Whisper project at the same time. 
A classical processing produces 8 TB in 5 days. Another computation 'read' 3 or 4 TB and 'produced' 1 TB in 6 hours.
Many tests of the signal processing are done and computational data are deleted as and when required.
\\

@@

The distributed storage accessible by all the computing nodes of all the clusters is managed by iRODS \footnote{see irods.org}.
Nowadays it represents approximately 700 TB. The grid computing is managed by the \emph{CiGri 
\footnote{see ciment.ujf-grenoble.fr/cigri/dokuwiki} middleware}, that is part of the OAR \footnote{see oar.imag.fr} project (the Resource and Job Management System on which CiGri relies). CiGri and iRODS together build a complementary solution for embarrassingly parallel computations with large input/output distributed data sets.

@@

Despite the problems that have been solved or not, we are currently able to process terabytes of data within a few hours, and product good scientific results in a reduced delay, therefore we may say that Whisper+CiGri+iRODS is a great success!

@@

@@

\bibitem{key:CCQSC}
 Gen-Tao Chiang, Peter Clapham, Guoying Qi, Kevin Sale and Guy Coates,
 Implementing a genomic data management system using iRODS in the Wellcome Trust Sanger Institute.
{\em BMC Bioinformatics,12(1):361+, September 2011.}

>>>>

\begin{document}
\long\def\/*#1*/{}
\date{}%{\today}
\title{\huge{DRAFT} \\ ~\\ \Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project}
\author{\begin{tabular}[t]{c@{\extracolsep{8em}}c}
	Briand Xavier\footnote{Cnrs, Isterre, Whisper, email xav.briand@gmail.com}  & Bzeznik Bruno\footnote{Ciment, Universit\'e Joseph Fourier, Technical header of Ciment} \\
\end{tabular}}
\maketitle
%\thispagestyle{empty}
\subsection*{Abstract}
{\em
Like many projects in science of the universe, the seismological project Whisper is faced with massive data processing.
This leads to specific IT software for the project as well as suitable IT infrastructure. We present here both aspects.

We provide a flexible way to design a sequence of processing. We also deal with data-management and computational optimization questions.
On IT infrastructure, we present the platform Ciment provided by the University of Grenoble. It offers a data-grid environement with the 
distributed storage iRODS and the grid manager CiGri.

This is the partnership between these two IT components that has enabled a data-intensive processing and, also,  permits to the Whisper project to bring new scientific results.
}
~\\ \\
{\bf Keywords}:  Data-Intensive, grid computing, distributed storage, Seismic Noise, Whisper, Cigri, Irods.

@@

\newpage
\section{Introduction}% 7-10\S, 1-2 pages}

@@

In addition, the calculation operations downstream may produce even more data than the observation data.
To give an order of magnitude, more than 200 TB have to be processed by the Whisper project at the same time. 
A classical processing produces 8 TB in 5 days. Another computation 'read' 3 or 4 TB and 'produced' 1 TB in 6 hours.
Many tests of the signal processing are done and computational data are deleted as and when required.

@@

The distributed storage accessible by all the computing nodes of all the clusters is managed by iRODS \footnote{see irods.org}.
Nowadays it represents approximately 700 TB. The grid computing is managed by the \emph{CiGri 
\footnote{see ciment.ujf-grenoble.fr/cigri/dokuwiki} middleware}, that is part of the OAR \footnote{see oar.imag.fr} \cite{key:CDGHMMNR, key:CHR2009} project (the Resource and Job Management System on which CiGri relies). CiGri and iRODS together build a complementary solution for embarrassingly parallel computations with large input/output distributed data sets.

@@

\section{Conclusion}

Despite the problems that have been solved or not, we are currently able to process terabytes of data within a few hours.

Note also that the local data grid (iRODS+CiGri) and more generally the platform of Ciment as well as the OAR tools permit for the Whisper project  to produce significant new results for seismological community in a reduced delay.

Lot of improvements that involve automatization of the processing, and also concerning the scientific workflow have constantly been made.

We may say that Whisper+CiGri+iRODS is a great success!

@@

\bibitem{key:CDGHMMNR}
Nicolas Capit, Georges Da Costa, Yiannis Georgiou, Guillaume Huard, Cyrille Martin, Gr\'egory Mouni\'e, Pierre Neyron, Olivier Richard,
A batch scheduler with high level components.
{\em Cluster computing and Grid 2005 (CCGrid05), Cardiff, Royaume-Uni, 2005.}

@@

\bibitem{key:CCQSC2005}
Gen-Tao Chiang, Peter Clapham, Guoying Qi, Kevin Sale and Guy Coates,
Implementing a genomic data management system using iRODS in the Wellcome Trust Sanger Institute.
{\em BMC Bioinformatics,12(1):361+, September 2011.}

\bibitem{key:CHR2009}
Beno\^it Claudel, Guillaume Huard, Olivier Richard,
TakTuk, Adaptive Deployment of Remote Executions.
{\em Proceedings of the International Symposium on High Performance Distributed Computing (HPDC) (2009) 91-100.}
